Blocking-resistant communication\\through domain fronting

### 2014-07-16 docs/meek.tex
Lantern.
Start a paragraph on Akamai.

Psiphon~\cite{psiphon} is a network of many one-hop proxies,
with encryption and traffic obfuscation between client and server.
Psiphon uses domain fronting based on meek as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.

% Lantern
% Infranet
% Freegate
% Ultrasurf
% Dust

@@

>>>>

Psiphon~\cite{psiphon} is a network of many one-hop proxies,
with encryption and traffic obfuscation between client and server.
Psiphon uses domain fronting based on meek as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.
Lantern~\cite{lantern} uses a network of proxies running on volunteer computers;
proxy addresses are shared only with trusted friends in order to make them difficult to enumerate.
Lantern~1.4 is planned to use domain fronting inspired by meek~\cite{lantern-1.3.1}.

% Infranet
% Freegate
% Ultrasurf
% Dust

@@

The collateral damage of blocking Akamai is enormous: in 2010 it carried 15--20\% of all web traffic~\cite{akamai}.
